---
title: "Project notepad"
subtitle: "For the project"
author: "David Goh"
format: pdf
editor: visual
---

## Packages

```{r}
#| label: load-pkgs
#| message: false
#| warning: false
 
library(tidyverse)
library(tidymodels)
library(knitr)
```

## Load data

```{r}
#| label: load-data
#| message: false

abortion_data <- read_csv("data/wvs-usa-abortion-attitudes-data.csv")
```

## Exploratory Data Analysis

Visualization and summary statistics for the response variable

``` {r visualization-summary}
ggplot(abortion_data, aes(x = aj)) +
  geom_histogram(binwidth = 1, aes(y=..density..)) + 
  geom_density(color = "red") +
  labs(title = "Histogram of attitudes full data set")

summary(abortion_data$aj)

```

## EDA on how to populate "ideology"

We will run all EDA on the set of responses that include ideology values and separately on the set of responses that do not in order to inform how we should populate those values.

``` {r visualize-ideology}

all_complete <- abortion_data[complete.cases(abortion_data),]

ggplot(all_complete, aes(x = aj)) +
  geom_histogram(binwidth = 1, aes(y=..density..)) + 
  geom_density(color = "red") +
  labs(title = "Histogram of attitudes only complete entries data set")
summary(all_complete$aj)

no_ideology <- abortion_data[!(abortion_data$ideology==""),]

ggplot(no_ideology, aes(x = aj)) +
  geom_histogram(binwidth = 1, aes(y=..density..))+ 
  geom_density(color = "red") +
  labs(title = "Histogram of attitudes excluding ideology=NA data set")
summary(no_ideology$aj)

```

## List of variables that will be considered as predictors

To discuss as group

## Run MLR on some variables

Just to show a preview of our analysis
